A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-10 doc/large_strain.tex
Relativize the 70%

{\color{red}
Figure \ref{fig:roofline} shows results of the roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $\pgfmathprintnumber{8.2093245}\,\rm{GFlop/s}$ (4.6\% of the peak performance) in 2D.
The matrix-free implementations of the fine-strain elastic tangent operator (on average) lead to a much better performance of
$\pgfmathprintnumber{18.8047083222}\,\rm{GFlop/s}$ in 2D, as well as about an order of magnitude higher computational intensity, but still stays in the memory-bound regime.
The achieved performance is about 10.6\% of the peak arithmetic performance. This is much lower than the
70\% reported for the Laplace operator on Cartesian meshes in \cite{kronbichler12}.
Unfortunately, performance measurements for non-Cartesian meshes were not reported in \cite{kronbichler12}.

>>>>

{\color{red}
Figure \ref{fig:roofline} shows results of the roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $\pgfmathprintnumber{8.2093245}\,\rm{GFlop/s}$ (4.6\% of the peak performance) in 2D.
The matrix-free implementations of the fine-strain elastic tangent operator (on average) lead to a much better performance of
$\pgfmathprintnumber{18.8047083222}\,\rm{GFlop/s}$ in 2D, as well as about an order of magnitude higher computational intensity, but still stays in the memory-bound regime.
The achieved performance is about 10.6\% of the peak arithmetic performance. This is much lower than the
70\% reported for the Laplace operator on Cartesian meshes in \cite{kronbichler12}, but similar to what was obtained in \cite[Figure 14]{kronbichler2017fast} when not optimizing for Cartesian meshes.
Unfortunately, performance measurements for non-Cartesian meshes were not reported in \cite{kronbichler12}.
